Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\medskip
As demonstrated by \citet{habermann_1960} \citep[see also][]{budek_2017}, mobility ratio (MR) is a key-parameter to assess fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
\begin{equation}
 \text{MR} \; = \frac{\mathcal{K}_{ri} \mu_{j}}{\mathcal{K}_{rj} \mu_{i}}. 
\label{eq:MR}
\end{equation}
MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix. In the simulations conducted for this work, the modified \cite{Brooks_1964} model was used \citep{alpak_1999},

>>>>

\medskip
As demonstrated by \citet{habermann_1960} \citep[see also][]{budek_2017}, mobility ratio (MR) is a key-parameter to assess fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
\begin{equation}
 \text{MR} \; = \frac{\mathcal{K}_{ri} \mu_{j}}{\mathcal{K}_{rj} \mu_{i}}. 
\label{eq:MR}
\end{equation}
MR is a function not only of fluids' viscosity, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix. In the simulations conducted for this work, the modified \cite{Brooks_1964} model was used \citep{alpak_1999},
